Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-14 introduction.tex
Added figures for sky localization paragraph
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1076 ccdd05d5-56c1-461a-bf98-85f6876523b4

Telescopic followup requires estimating the location of the \GW{} source. The
localization uncertainty is dominated by uncertainty in the time of arrival of
the \GW{}s, which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}. Unfortunately, for a \GW{} signal with an \SNR{} of
blah, the 90\% confidence area is at least blah deg$^2$ (blah\% of the sky) at
10~s before merger and blah deg$^2$ (blah\% of the sky) at 1~s before merger.
It is infeasible to search this large an area for a prompt counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.

>>>>

Telescopic followup requires estimating the location of the \GW{} source. The
localization uncertainty is dominated by uncertainty in the time of arrival of
the \GW{}s, which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}. Unfortunately, for a \GW{} signal with an \SNR{} of
10, the 90\% confidence area is at least $2 \times 10^3$~deg$^2$ (4.8\% of the sky) at
10~s before merger and $10^2$~deg$^2$ (0.3\% of the sky) at 1~s before merger.
It is infeasible to search this large an area for a prompt counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.
